RMD file for Group 1 Analysis

<<<<<<< HEAD
Loading the required libraries
```{r}
library(tidyverse)
library(dplyr)
```

Loading the dataset

```{r}
gtd <- read_csv("globalterrorismdb_0718dist.csv")
head(gtd)
```

=======
```{r}

#| label: role 1

pacman::p_load(tidyverse,
               dplyr,
               ggplot2)
            
gtd <- read.csv("globalterrorismdb_0718dist.csv")
head(gtd)

gtd_filter <- gtd |>
  filter(!is.na(iyear))
gtd_filter

#| label: role 2

attacks_per_year <- gtd_filter |>
  group_by(iyear) |>
  summarise(total_attacks = n())
attacks_per_year

```
>>>>>>> 91d2fb79679973ba7cd1b9c2d9c87b9eb4ac7616

```{r}
attacks_per_year
```


```{r fig.height = 10}

#| label: role 3

# Visualizing the number of attacks per year using a bar chart.

attacks_barchart <- ggplot(attacks_per_year, aes(x = as.factor(iyear), y = total_attacks)) +
geom_bar(stat = "identity", fill = "purple3") +
  labs(title = "Bar chart showing number of Attacks per Year",
       x = "Year",
       y = "Number of Attacks") +
  theme( axis.text.x = element_text(angle = 180, hjust = 1, vjust = 0.5)) +
  theme_minimal()

plot(attacks_barchart)
```





